### 2017-11-12 Draft2/Appendix.tex
Finish with all the proofs...

\begin{proof}[Proof (Theorem \ref{thm:MergesOverOps})]
	% TODO: Prove statement for addition.

	The statement about multiplication is more easily proven. Since both $\ExprNToInfty \dfrac{f}{\Tweak{f}}$ and $\ExprNToInfty \dfrac{g}{\Tweak{g}}$ exist,
	\begin{align*}
	\ExprNToInfty \frac{fg}{\Tweak{f}\Tweak{g}} = \left( \ExprNToInfty \frac{f}{\Tweak{f}} \right) \left( \ExprNToInfty \frac{g}{\Tweak{g}} \right) = 1 \cdot 1 = 1
	\end{align*}
	It follows that $fg \sim \Tweak{f}\Tweak{g}$. If the limit for $g$ is flipped before multiplying, the following results:
	\begin{align*}
	\ExprNToInfty \frac{f / g}{\Tweak{f} / \Tweak{g}} = 1
	\end{align*}
	This shows that $\dfrac f g \sim \dfrac {\Tweak{f}} {\Tweak{g}}$.
\end{proof}

>>>>

\begin{proof}[Proof (Theorem \ref{thm:MergesOverOps})]
	Let $\FuncQuotient = \dfrac{f + g}{\Tweak{f} + \Tweak{g}}$, and let $\FuncDenom = \Tweak{g} + \Tweak{g}^2 / \Tweak{f}$. $\FuncQuotient$ may be expressed as
	\begin{align*}
	\FuncQuotient &= \frac{(\Tweak{g} / \Tweak{f})(f + g)}{(\Tweak{g} / \Tweak{f})(\Tweak{f} + \Tweak{g})}\\
	&= \frac{\Tweak{g}(f / \Tweak{f}) + \Tweak{g}g / \Tweak{f}}{\FuncDenom}\\
	&= \frac{\Tweak{g}(f / \Tweak{f}) + (\Tweak{g}^2 / \Tweak{f})(g / \Tweak{g})}{\FuncDenom}\\
	&= \frac{\Tweak{g}}{d} \cdot \frac{f}{\Tweak{f}} + \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \frac{g}{\Tweak{g}}
	\end{align*}
	Now, consider that
	\begin{align*}
	\FuncQuotient - 1 &= \FuncQuotient - \frac{\FuncDenom}{\FuncDenom} = \FuncQuotient - \frac{\Tweak{g}}{\FuncDenom} - \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom}\\
	&= \frac{\Tweak{g}}{d} \cdot \frac{f}{\Tweak{f}} + \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \frac{g}{\Tweak{g}} - \frac{\Tweak{g}}{\FuncDenom} - \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom}\\
	&= \frac{\Tweak{g}}{d} \cdot \left( \frac{f}{\Tweak{f}} - 1 \right) + \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \left( \frac{g}{\Tweak{g}} - 1 \right)\\
	\ExprNToInfty \left( \FuncQuotient - 1 \right) &= \ExprNToInfty \left( \frac{\Tweak{g}}{d} \cdot \left( \frac{f}{\Tweak{f}} - 1 \right) + \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \left( \frac{g}{\Tweak{g}} - 1 \right) \right)\\
	&= \ExprNToInfty \left( \frac{\Tweak{g}}{d} \cdot \left( \frac{f}{\Tweak{f}} - 1 \right) \right) + \ExprNToInfty \left( \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \left( \frac{g}{\Tweak{g}} - 1 \right) \right)
	\end{align*}
	Since $\Tweak{g}$ and $\Tweak{g}^2 / \Tweak{f}$ sum to $\FuncDenom$ and all functions are positive, $\dfrac{\Tweak{g}}{\FuncDenom}$ and $\dfrac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom}$ are bounded between $0$ and $1$ as $n \to \infty$. From the given, $\ExprNToInfty \left( \dfrac{f}{\Tweak{f}} - 1 \right)$ and $\ExprNToInfty \left( \dfrac{g}{\Tweak{g}} - 1 \right)$ both exist and equal $0$. The limit of a bounded expression times one approaching $0$ is $0$; thus, both limits on the right-hand side are $0$.

	Substituting, I receive $\ExprNToInfty (\FuncQuotient - 1) = 0$, so $\ExprNToInfty \FuncQuotient = 1$. Since $\FuncQuotient$ is defined as $\dfrac{f + g}{\Tweak{f} + \Tweak{g}}$, this shows that $f + g \sim \Tweak{f} + \Tweak{g}$, proving the theorem statement for addition.

	The statement is much more easily proven for multiplication. Since both $\ExprNToInfty \dfrac{f}{\Tweak{f}}$ and $\ExprNToInfty \dfrac{g}{\Tweak{g}}$ exist,
	\begin{align*}
	\ExprNToInfty \frac{fg}{\Tweak{f}\Tweak{g}} = \left( \ExprNToInfty \frac{f}{\Tweak{f}} \right) \left( \ExprNToInfty \frac{g}{\Tweak{g}} \right) = 1 \cdot 1 = 1
	\end{align*}
	It follows that $fg \sim \Tweak{f}\Tweak{g}$. If the limit for $g$ is flipped before multiplying, the following results:
	\begin{align*}
	\ExprNToInfty \frac{f / g}{\Tweak{f} / \Tweak{g}} = 1
	\end{align*}
	This implies that $\dfrac f g \sim \dfrac {\Tweak{f}} {\Tweak{g}}$.
\end{proof}
